Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-10 hpmoon-asoco.tex
Fixing the generation-gap paragraph

The number of generations between migrations has been set to 5,
\textcolor{blue} as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, we make the system closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, we make the isolate islands more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the chromosome, so while we tend to agree with
Martens on the small influence of this value on the result, we also
think that making this value much bigger in our case would havea
negative inpact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to prove the
general concept, and not tune the values for a maximum performance}.

>>>>

The number of generations between migrations has been set to 5,
\textcolor{blue}{as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
and as affirmed by 
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, we make the system closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, we make the isolate islands more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the chromosome, so while we tend to agree with
Martens on the small influence of this value on the result, we also
think that making this value much bigger in our case would have a
negative impact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to prove the
general concept, and not tune the values for a maximum performance}.
